Computing astrophysical inferences with diffusive nested sampling

### 2014-03-06 ms.tex
Minor writing

Computing the consequences of a posterior distribution can be a challenging
task. Usually we want to marginalise out nuisance parameters, to compute
particular posterior probabilities such as $P(\theta > 1.5)$, or to summarise
the posterior distribution for easy communication with others.
Markov Chain Monte Carlo (MCMC) algorithms provide a general set of tools
for achieving these goals. However, many standard MCMC algorithms are not
capable of exploring complicated probability distributions in a reasonable time.
Problems often occur due to multimodality, strong dependencies, and phase
transitions. Many different solutions have been suggested for overcoming these
challenges. In this paper we will focus on Nested Sampling \citep{skilling}.

\section{Nested sampling}
The key idea of Nested Sampling \citep{skilling} is that Bayesian computation
should begin from the prior $\pi(\pars)$ and move through a sequence of
distributions that successively compress the prior volume by a constant factor
that is (approximately) known.

>>>>

Computing the consequences of a posterior distribution can be a challenging
task. Usually we want to marginalise away nuisance parameters, to compute
particular posterior probabilities such as $P(\theta > 1.5)$, or to summarise
the posterior distribution for easy communication with others, for example by
calculating credible intervals and stating that $a \leq \theta b$ with 95\%
probability.
Markov Chain Monte Carlo (MCMC) algorithms provide a general set of tools
for achieving these goals. However, many standard MCMC algorithms are not
capable of exploring complicated probability distributions in a reasonable time.
Problems often occur due to multiple modes, strong dependencies
between parameters, and (less widely recognised, but also less commonly) phase
transitions. Many different solutions have been suggested for overcoming these
challenges. This paper focuses on Nested Sampling \citep{skilling}.

\section{Nested sampling}
The key idea of Nested Sampling \citep{skilling} is that Bayesian computation
should not solely be aimed at obtaining samples from the posterior distribution.
By beginning from the prior $\pi(\pars)$ and moving through a sequence of
distributions that successively compress the prior volume by a constant factor
that is (approximately) known, Nested Sampling can calculate posterior samples
as well as the marginal likelihood or evidence
$Z = \int p(\pars)p(\data = \data_{\rm actual} | \pars) \, d\pars$.
